### 2024-05-30 2024-5-13/sections/implementation.tex
change experiments

\subsection{Empirical justification of the technical choices and heuristics}\label{subsec:size_reduction_eval}
We also do experiments to evaluate the effectiveness of the automata size-reduction techniques, that is, Step 2 of Section~\ref{subsec:cefadec}. We practically answer why we choose LIA formula to solve the nonemptiness problem instead of using the nuXmv model checker like \cite{atva2020}. Finally, we carry out experiment on the ComplexCounting benchmarks to justify the heuristics of Section~\ref{sec:heuristic}.
\subsubsection{Empirical justification of the technical choices}
%We also do experiments to evaluate the effectiveness of the automata size-reduction techniques, that is, Step 2 in Section~\ref{subsec:cefadec}. 
%Let us use $\ostrichrecl_{\rm -SIMP}$ to denote $\ostrichrecl$ with the size-reduction techniques removed. 
We compare $\ostrichrecl$ with its variants ${\rm -ASR}$ and ${\rm +NUXMV}$. ${\rm -ASR}$ is obtained from $\ostrichrecl$ by removing the automata size-reduction technique (i.e. Step 2 of Section~\ref{subsec:cefadec}). ${\rm +NUXMV}$ uses the nuXmv model checker to solve the nonemptiness of $\cefadec$.

The experiment results can be found in Table~\ref{tab:results_heuristic}.
We can see that $\ostrichrecl$ solves 1,083 more instances and is 1.65 times faster than ${\rm -ASR}$. Therefore,  the automata size-reduction technique indeed plays an essential role in the performance improvement.
We can see that $\ostrichrecl$ solves 2,532 more instances and is 2.38 times faster than ${\rm +NUXMV}$. Therefore, the decision procedure in Section~\ref{subsec:cefadec} is more efficient to solve the $\cefadec$ problem than nuXmv. 
\begin{table}
  \import{tables}{table_heuristics.tex}
  \caption{Empirical justification of the technical choices and heuristics}\label{tab:results_heuristic}
\end{table}

\subsubsection{Empirical justification of the heuristics} 
We also compare the performance of $\ostrichrecl$ with its variants ${\rm -NEST}$, ${\rm -COMP}$, ${\rm -FIND}$. ${\rm -NEST}$ is obtained from $\ostrichrecl$ by removing the heuristic for nested counting. ${\rm -COMP}$ is obtained by removing the heuristic for complement on counting operators. ${\rm -FIND}$ is obtained by removing the heuristic for finding the accepted word of the automaton.

>>>>

\subsection{Empirical justification of the technical choices and heuristics}\label{subsec:size_reduction_eval}
We also do experiments to evaluate the effectiveness of the automata size-reduction techniques for register-representable regexes, that is, Step 2 of Section~\ref{subsec:cefadec}. We practically answer why we choose LIA formula to solve the nonemptiness problem instead of using the nuXmv model checker like \cite{atva2020}. Finally, we carry out experiment on the ComplexCounting benchmarks to justify the heuristics of Section~\ref{sec:heuristic} for non-register-representable regexes.
\subsubsection{Empirical justification of the technical choices}
%We also do experiments to evaluate the effectiveness of the automata size-reduction techniques, that is, Step 2 in Section~\ref{subsec:cefadec}. 
%Let us use $\ostrichrecl_{\rm -SIMP}$ to denote $\ostrichrecl$ with the size-reduction techniques removed. 
We compare $\ostrichrecl$ with its variant  ${\rm +NUXMV}$. ${\rm +NUXMV}$  is obtained from $\ostrichrecl$ by using the nuXmv model checker to solve the nonemptiness of $\cefadec$.

The experiment results can be found in Table~\ref{tab:results_heuristic}. We can see that $\ostrichrecl$ solves 2,532 more instances and is 2.38 times faster than ${\rm +NUXMV}$. Therefore, the decision procedure in Section~\ref{subsec:cefadec} is more efficient to solve the $\cefadec$ problem than nuXmv. 
\begin{table}
  \import{tables}{table_heuristics.tex}
  \caption{Empirical justification of the technical choices and heuristics}\label{tab:results_heuristic}
\end{table}

\subsubsection{Empirical justification of the size-reduction technique for register-representable regexes}
We compare $\ostrichrecl$ with its variant ${\rm -ASR}$.  ${\rm -ASR}$ is obtained from $\ostrichrecl$ by removing the automata size-reduction technique (i.e. Step 2 of Section~\ref{subsec:cefadec}). 
The experiment results can be found in Table~\ref{tab:results_heuristic}. We can see that $\ostrichrecl$ solves 1,083 more instances and is 1.65 times faster than ${\rm -ASR}$. Therefore,  the automata size-reduction technique indeed plays an essential role in the performance improvement.

\subsubsection{Empirical justification of the heuristics for non-regesiter-representable regexes} 
We also compare the performance of $\ostrichrecl$ with its variants ${\rm -NEST}$, ${\rm -COMP}$, ${\rm -FIND}$. ${\rm -NEST}$ is obtained from $\ostrichrecl$ by removing the heuristic for nested counting. ${\rm -COMP}$ is obtained by removing the heuristic for complement on counting operators. ${\rm -FIND}$ is obtained by removing the heuristic for finding the accepted word of the automaton.
